Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-08 resolution.tex
edits

The global mean, climatological components $\langle f_{u} \rangle \, \langle \omega_{u} \rangle$ and $\langle f_{d} \rangle \, \langle \omega_{d} \rangle$ are provided in Figure~\ref{fig:4panel}a,b for the aqua-planet simulations. The magnitude of both $\langle f_{u} \rangle \, \langle \omega_{u} \rangle$ and $\langle f_{d} \rangle \, \langle \omega_{d} \rangle$ increase monotonically with resolution, and are both equal and opposite, which is a requirement of mass conservation in the model and a convenient check of the calculation. The individual component $\langle f_{x} \rangle$ varies by only few percent in the simulations, and so the monotonic behavior of $\langle f_{x} \rangle \, \langle \omega_{x} \rangle$ is primarily due to $ \langle \omega_{x} \rangle$ (not shown).

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_diags_4panel.pdf}\\
\end{center}
\caption{(a,b,c,e,f,g) Components of the global mean vertical pressure velocity $\overline{\langle \omega \rangle}$ (d) ratio of global mean ZM precipitation rate to the total precipitation rate versus grid spacing $\Delta x$ and (e) scatter plot of $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$ and FREQZM, and the fitted linear regression which has a Pearson's R-value = 0.99. (a) $\overline{\langle \omega_{u} \rangle}$ (b) $\overline{\langle f_{u} \rangle}$ (c) $\overline{\langle f_{u} \rangle} \, \overline{\langle \omega_{u} \rangle}$ (e) $\overline{\langle \omega_{d} \rangle}$ (f) $ \overline{\langle f_{d} \rangle}$ (g) $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$. Colors are as in Figure~\ref{fig:2pdf}. Grey crosses are for the perturbed parameter runs.}
\label{fig:4panel}
\end{figure}

@@

>>>>

The global mean, climatological components $\langle f_{u} \rangle \, \langle \omega_{u} \rangle$ and $\langle f_{d} \rangle \, \langle \omega_{d} \rangle$ are provided in Figure~\ref{fig:2panel}a,b for the aqua-planet simulations. The magnitude of both $\langle f_{u} \rangle \, \langle \omega_{u} \rangle$ and $\langle f_{d} \rangle \, \langle \omega_{d} \rangle$ increase monotonically with resolution, and are both equal and opposite, which is a requirement of mass conservation in the model and a convenient check of the calculation. The individual component $\langle f_{x} \rangle$ varies by only few percent in the simulations, and so the monotonic behavior of $\langle f_{x} \rangle \, \langle \omega_{x} \rangle$ is primarily due to $ \langle \omega_{x} \rangle$ (not shown).

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_diags_2panel.pdf}\\
\end{center}
\caption{(a,b,c,e,f,g) Components of the global mean vertical pressure velocity $\overline{\langle \omega \rangle}$ (d) ratio of global mean ZM precipitation rate to the total precipitation rate versus grid spacing $\Delta x$ and (e) scatter plot of $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$ and FREQZM, and the fitted linear regression which has a Pearson's R-value = 0.99. (a) $\overline{\langle \omega_{u} \rangle}$ (b) $\overline{\langle f_{u} \rangle}$ (c) $\overline{\langle f_{u} \rangle} \, \overline{\langle \omega_{u} \rangle}$ (e) $\overline{\langle \omega_{d} \rangle}$ (f) $ \overline{\langle f_{d} \rangle}$ (g) $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$. Colors are as in Figure~\ref{fig:2pdf}. Grey crosses are for the perturbed parameter runs.}
\label{fig:2panel}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_diags_corr.pdf}\\
\end{center}
\caption{Scatter plot of $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$ and FREQZM, and the fitted linear regression which has a Pearson's R-value = 0.99. Colors are as in Figure~\ref{fig:2pdf}. Grey crosses are for the perturbed parameter ensemble.}
\label{fig:corr}
\end{figure}
